---
title: |
  | Wadi Al Sulai
  | Construction Management
  | List Report
author:
- Amanah Riyadh
- Boedeker Landscape Architects
header-includes:
- \usepackage{graphicx}
- \usepackage{fancyhdr}
- \pagestyle{fancy}
- \setlength\headheight{28pt}
- \fancyhead[L,CE]{\includegraphics[width=1cm]{WS-logo.png} Wadi Al Sulai Construction Management}
- \fancyhead[R,CE]{\includegraphics[width=2cm]{bpla-logo-220.png}}
- \fancyfoot[L,CE]{`r format(Sys.time(), '%d %B %Y')`}
- \fancyfoot[R,CE]{Boedeker Landscape Architects}
output:
  pdf_document:
    #fig_height: 1
    #fig_width: 1
    #keep_tex: yes
    #highlight: tango
    latex_engine: xelatex
    number_sections: yes
    # toc: yes
#mainfont: Arial
classoption: report
---

```{r 'setup', collapse=F, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE,
                      results = 'asis')
```

# Construction activities

In the period of `r format(min(as.Date(apidata()$Created)), '%d.%m.%Y')` to `r format(max(as.Date(apidata()$Created)), '%d.%m.%Y')` site supervision activities have been documented.  `r nrow(apidata())` activities were recorded with the following status.

```{r 'abstract', echo=FALSE, message=TRUE, warning=TRUE, results='asis'}
statusTable <- t(table(datain()$Status))
# #colnames(status.table)[1]
knitr::kable(statusTable, format="markdown", row.names = F, align = 'c')
```


# Selected activities
This report shows `r nrow(datain())` recordings out of the total number of records based on the following selection: 

* Responsible: `r input$responsible`
* Date: `r format(input$dateRange[1], '%d.%m.%Y')` to `r format(input$dateRange[2], '%d.%m.%Y')`
* Item:  `r input$issue` 
* Status: `r input$status`

\newpage
## Report of selected activities
```{r 'img table', results='asis', echo=FALSE}
#make image captions
imageta<-datain()[,c("ID","KM","Status","Issue","photos_url")]
imageta$capt<-paste0(imageta$Status,": ",imageta$ID)
imageta$capt1<-paste0(imageta$KM,"KM: ",imageta$Issue)
imageta$capt2<-""
#make table
if (nrow(imageta) %%3 !=0){
    b = t(c(imageta[,c("photos_url")],rep(x="",times=(3-nrow(imageta) %%3))))
    c = t(c(imageta[,c("capt")],rep(x="",times=(3-nrow(imageta) %%3))))
    c1 = t(c(imageta[,c("capt1")],rep(x="",times=(3-nrow(imageta) %%3))))
    c2 = t(c(imageta[,c("capt2")],rep(x="",times=(3-nrow(imageta) %%3))))
}else{
    b = t(imageta[,c("photos_url")])
    c = t(imageta[,c("capt")])
    c1 = t(imageta[,c("capt1")])
    c2 = t(imageta[,c("capt2")])
}

# b<-c(b,rep("",3))
# c<-c(c,rep("",3))
# c1<-c(c1,rep("",3))
# c2<-c(c2,rep("",3))

d=rbind(b,c,c1,c2)
e=matrix(d,ncol = 3,byrow=F)
colnames(e)<-c("","","")
#e<-t(e)
knitr::kable(e, format = "markdown", caption = '',longtable=T, row.names = F)
#padding=c(10,10,0), align='c'
```