---
title: |
  | Wadi Al Sulai
  | Construction Management
  | List Report
author:
- Amanah Riyadh
- Boedeker Landscape Architects
header-includes:
#font mess
- \usepackage{fontspec}
- \setmainfont{Calibri.sty}
#- \defaultfontfeatures{Mapping=tex-text}
# - \usepackage{xunicode}
# - \usepackage{xltxtra}
# - \setmainfont{Calibri}
# # - \usepackage[scaled]{helvet}
# # - \renewcommand*\familydefault{\sfdefault}
# - \RequirePackage{fontenc}
# - \usepackage[T1]{fontenc}
# - \usepackage{fontenc}
# - \usepackage[utf8]{inputenc}
# - \RequirePackage{sysfonts}
# #- \usepackage{sysfonts}
# - \setmainfont{\fontspec{Calibri.}}
#- \usepackage{Verdana}
# - \setmainfont{texgyrepagella-regular.otf}[ BoldFont = texgyrepagella-bold.otf , ItalicFont = texgyrepagella-italic.otf , BoldItalicFont = texgyrepagella-bolditalic.otf ]
# - \RequirePackage{Verdana}
# - \setmainfont{\fontspec{Calibri}}
# - \setsansfont{Trebuchet MS} 
# - \setmonofont{Inconsolata}
#- \setmainfont{Verdana}
#- \usepackage[T1]{fontenc}
#- \usepackage[utf8]{inputenc}
#- \setmainfont{Arial}
- \usepackage{graphicx}
- \usepackage{fancyhdr}
- \pagestyle{fancy}
- \setlength\headheight{28pt}
- \fancyhead[L,CE]{\includegraphics[width=1cm]{WS-logo.png} Wadi Al Sulai Construction Management}
- \fancyhead[R,CE]{\includegraphics[width=2cm]{bpla-logo-220.png}}
- \fancyfoot[L,CE]{`r format(Sys.time(), '%d %B %Y')`}
- \fancyfoot[R,CE]{Boedeker Landscape Architects}
output:
  pdf_document:
    latex_engine: xelatex
    number_sections: yes
    keep_tex: yes
classoption: report
papersize: A4
geometry:
    margin=0.5in
#fontfamily: Arial
#mainfont: Arial
---


```{r 'setup', collapse=F, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE,
                      results = 'asis')
#options(width = 8)
```

# Construction activities

In the period of `r format(min(as.Date(apidata()$Created)), '%d.%m.%Y')` to `r format(max(as.Date(apidata()$Created)), '%d.%m.%Y')` site supervision activities have been documented.  `r nrow(apidata())` activities were recorded with the following status.

```{r 'abstract', echo=FALSE, message=TRUE, warning=TRUE, results='asis'}
statusTable <- t(table(datain()$Status))
# #colnames(status.table)[1]
knitr::kable(statusTable, format="markdown", row.names = F, align = 'c')
```


# Selected activities

This report shows `r nrow(datain())` recordings out of the total number of records based on the following selection: 

* Responsible: `r input$responsible`
* Date: `r format(input$dateRange[1], '%d.%m.%Y')` to `r format(input$dateRange[2], '%d.%m.%Y')`
* Issue:  `r input$issue` 
* Status: `r input$status`


\newpage
## Report of selected activities
<!-- The table below shows the `r input$actionrequired` in the period from `r input$dateRange[1]`ot `r input$dateRange[2]` with the species  `r input$species` and the status `r input$status`. -->
```{r 'table1', results='asis', echo=FALSE,fig.width = 12}
tabledata<-datain()[,c("ID","KM","Status","Issue","Action","Comments","Created")]
tabledata$Created<-format(as.Date(tabledata$Created), "%d.%m.%Y")
knitr::kable(tabledata, format = "markdown",longtable = TRUE, row.names = F,booktabs =T, padding = c(10,10,60,20,0,60,40))
#padding for Arial padding = c(10,10,40,10,0,10,10)
```