---
title: |
  | Wadi Al Sulai
  | Construction Management
  | List Report
author:
- Amanah Riyadh
- Boedeker Landscape Architects
date: "Report generated: `r format(Sys.time(), '%d %B %Y at %H:%M:%S')`"
header-includes:
#font mess
- \usepackage[scaled]{helvet}
- \renewcommand*\familydefault{\sfdefault}
- \usepackage[T1]{fontenc}
- \usepackage{graphicx}
- \usepackage{fancyhdr}
- \pagestyle{fancy}
- \setlength\headheight{28pt}
- \fancyhead[L,CE]{\includegraphics[width=1cm]{WS-logo.png}} 
- \fancyhead[C]{\centering {Wadi Al Sulai Construction Management}}
- \fancyhead[R,CE]{\includegraphics[width=2cm]{bpla-logo-220.png}}
- \fancyfoot[L,CE]{`r format(Sys.time(), '%d %B %Y')`}
- \fancyfoot[R,CE]{Boedeker Landscape Architects}
output:
  pdf_document:
    latex_engine: xelatex
    number_sections: yes
    #keep_tex: yes
classoption: article
papersize: A4
fontsize: 11pt
geometry: margin=0.8in
linestretch: 1.15
# geometry:
#     margin: 0.5in
---


```{r 'setup', collapse=F, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE,
                      results = 'asis')
#options(width = 8)
```

# Construction activities

In the period of `r format(min(as.Date(apidata()$Created)), '%d.%m.%Y')` to `r format(max(as.Date(apidata()$Created)), '%d.%m.%Y')` site supervision activities have been documented.  `r nrow(apidata())` activities were recorded with the following status.

```{r 'abstract', echo=FALSE, message=TRUE, warning=TRUE, results='asis'}
statusTable <- t(table(datain()$Status))
# #colnames(status.table)[1]
knitr::kable(statusTable, format="markdown", row.names = F, align = 'c')
```


# Selected activities

This report shows `r nrow(datain())` recordings out of the total number of records based on the following selection: 

* Responsible: `r input$responsible`
* Date: `r format(input$dateRange[1], '%d.%m.%Y')` to `r format(input$dateRange[2], '%d.%m.%Y')`
* Issue:  `r input$issue` 
* Status: `r input$status`


\newpage
## Report of selected activities
<!-- The table below shows the `r input$actionrequired` in the period from `r input$dateRange[1]`ot `r input$dateRange[2]` with the species  `r input$species` and the status `r input$status`. -->
```{r 'table1', results='asis', echo=FALSE,fig.width = 12}
tabledata<-datain()[,c("ID","KM","Status","Issue","Action","Comments","Created")]
tabledata$Created<-format(as.Date(tabledata$Created), "%d.%m.%Y")
knitr::kable(tabledata, format = "markdown",longtable = TRUE, row.names = F,booktabs =T, padding = c(10,10,60,20,0,60,40))
#padding for Arial padding = c(10,10,40,10,10,10,10)
```